

---
title: "Working from self-driving car - parameters for Monte-Carlo Simulation"
author: "Georg Hirte"
date: "20 01 2023"
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
header-includes: \usepackage{graphicx, xcolor, hyperref, natbib, eurosym} 
  \setcitestyle{authoryear,
  open={(},close={)}}
---


```{r message=FALSE, warning=FALSE, results="hide", setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#::opts_chunk$set(comment = NA, echo=FALSE, message = FALSE, warnings = FALSE, results = 'hide')
#RStudio 2021.09.0 Build 351
# R version 4.1.2.
```
# 1. Introduction
We calculate the parameters required in the Monte-Carlo Simulation of the paper 
``Working from self-driving car'' by Georg Hirte. 

* If we have **one observation** far away from zero, we assume this is the mean 
of a normal distribution with a standard deviation we arbitrarily choose, or a 
uniform distribution with arbitrarily chosen supports. If the observation is 
right-skewed and has a left truncation at zero, we use a Gamma distribution. 
We take 10,000 draws from these distributions.
* If we have **two or more data points** we either use them as limits of a 95% 
confidence interval of a normal distribution, the mean supports of a 
truncated distribution, supports and mean of a Gamma distribution, or support of
a uniform distribution

* Further restrictions are considered as they come along.


# 2. Install and load libraries

Clear data
```{r, results="hide", warning=FALSE,  message="FALSE"}
rm(list=ls(all=T))
graphics.off()
```

Install packages
```{r 0.0.0 install packages, results="hide", warning=FALSE,  message="FALSE"}
install.packages("C:/Users/Hirte/Aufsatz/AutonomCarOffice/GAMS_InVehicleWork/gdxrrw_1.0.6.zip"
                 ,repos=NULL, type = "win.binary")
## next: truncated normal distribution and truncated distributions
#install.packages("truncnorm","crch")
#install.packages("UnivRNG")
#source("install.r")
#install.packages('kerdiest')
#install.packages("stargazer")
#to read GDX files we need the gdxrrw package

library(reshape2);
library(ggplot2);
# url <- "http://cran.r-project.org/src/contrib/Archive/mcsm/mcsm_1.0.tar.gz"
# pkgFile <- "mcsm_1.0.tar.gzz"
# download.file(url = url, destfile = pkgFile)
# # Expand the zip file using whatever system functions are preferred
# # look at the DESCRIPTION file in the expanded package directory
# # Install dependencies list in the DESCRIPTION file
# install.packages(c("coda","stats","MASS"))
# # Install package
# install.packages(pkgs=pkgFile, type="source", repos=NULL)
# # Delete package tarball
# unlink(pkgFile)


library("mcsm");
library("pastecs");
library(truncnorm);
library(crch);
library(UnivRNG);
library(gdxrrw);
igdx("")
#igdx("c:/GAMS/34/");
igdx("c:/GAMS/41/");
install.packages('gdxdt')
# next: left truncated gamma
rm(list=ls())
```
## Definitions and Functions

```{r,definitions}
## Calculate the parameters with cut-offs (interval) and mean used in MC simulation
# we apply a truncated normal distribution

# Definitions
## number of random draws
numberrandom <- 10000
kmmile <- 1.60934
# 23.03.2021
EURDollar <- 0.84
# sqft per sqm
sqmsqft <- 10.7639



# Define plot gamma distribution 
# 
# ## Calculate the parameters with cut-offs (interval) and mean used in the MC 
# if distance between mean and cut-offs is not symmetric we apply a gamma distribution
# if parameters must be non-negative we also apply a gamma distribution
# 1. fit a gamma distribution to parameters (mean and interval) 
# 2. make 10000 draws from this distribution

# Fit a gamma distribution knowing that:
# - 20% fall below 15 - only start values here
# - 80% fall below 60 - only start values here
# Inspired by http://www.johndcook.com/blog/2010/01/31/parameters-from-percentiles/
# x <- c(0.2, 0.8)
# y <- c(15, 60)
# # ?dgamma
# # ?qgamma
# 
# # plot the gamma curve for a given shape and rate argument ----------------
# 
# # draws vertical lines at p
 plotGamma <- function(shape=2, rate=0.5, to=0.99, p=c(0.1, 0.9), cex=1, ...){
   to <- qgamma(p=to, shape=shape, rate=rate)
   curve(dgamma(x, shape, rate), from=0, to=to, n=500, type="l", 
         main=sprintf("gamma(x, shape=%1.2f, rate=%1.2f)", shape, rate),
         bty="n", xaxs="i", yaxs="i", col="blue", xlab="", ylab="", 
         las=1, lwd=2, cex=cex, cex.axis=cex, cex.main=cex, ...)
   gx <- qgamma(p=p,  shape=shape, rate=rate)
   gy <- dgamma(x=gx, shape=shape, rate=rate)
   for(i in seq_along(p)) { lines(x=rep(gx[i], 2), y=c(0, gy[i]), col="blue") }
   for(i in seq_along(p)) { text(x=gx[i], 0, p[i], adj=c(1.1, -0.2), cex=cex) }
 };

 plotGamma2 <- function(shape=2, rate=0.5, to=0.99, p=c(0.1, 0.9), cex=1, ngy=c(1.0), ...){
   to <- qgamma(p=to, shape=shape, rate=rate)
   curve(dgamma(x, shape, rate), from=0, to=to, n=500, type="l", 
         main=sprintf("gamma(x, shape=%1.2f, rate=%1.2f)", shape, rate),
         bty="n", xaxs="i", yaxs="i", col="blue", xlab="", ylab="", 
         las=1, lwd=2, cex=cex, cex.axis=cex, cex.main=cex, ...)
   gx <- qgamma(p=p,  shape=shape, rate=rate)
   gy <- dgamma(x=gx, shape=shape, rate=rate) * ngy
   for(i in seq_along(p)) { lines(x=rep(gx[i], 2), y=c(0, gy[i]), col="blue") }
   for(i in seq_along(p)) { text(x=gx[i], 0, p[i], adj=c(1.1, -0.2), cex=cex) }
 };
 

# formulate a gamma error function for non-linear least squares -----------
# from http://www.r-bloggers.com/parameters-and-percentiles-the-gamma-distribution/
errorGamma <- function(p=c(10,3), quantiles, exp){
  gx <- c(qgamma(p=quantiles, shape=p[1], rate=p[2]))
  sum((gx-exp)^2)
};
```


# 3. Travel parameters

## 3.1 Commuting costs per VKT: gkm

### 3.1.1 pargkmDE

pargkmDE $\equiv$  avg. private travel cost per km by car () in Germany

**Use truncated normal distribution** 

* \citet{ADAC2020a} compares 73 electric cars ($N=73$) with hybrid and conventional 
cars (CV). 15000 VKT per year.
* Results do not consider electricity tax (tax free until 2030. Electricity tax 
in Germany is 0.0205 EUR/kWh, \citep{StromStG} $\rightarrow$ 0.0037 EUR/km given 
consumption of 18 kWh/100km)
* Assumptions: current prices; lowest 30.6 (CitiGo e IV Ambition von Skoda, 
lower limit: lower1) and highest 120.8 (Model X Performance von Tesla, upper limit: upper1) 
are borders of the symmetric 95% confidence intercal CI
* CI is $2 \times 1.96$ s.e. wide in case of a normal distributon, $\mu =1/2 * (0.306+1.208)$ 
  $$\rightarrow sd = sqrt(N) * (\text{upperlimit} - \text{lowerlimit})/3.92$$ 
* 10000 (numberrandom) draws from the truncated normal distribution

```{r,gkmDE}
# lower bound
lower1 <- 0.306
lower1
# upper bound of the truncation
upper1 <- 1.208
upper1
# mean and sd if symmetric
mean1 <- 1/2 * (lower1 + upper1)
mean1
# observations
nn <- 
# lower1 is the 2.5% percentile of a normal distribution
#sd1 <- (lower1-mean1)/qnorm(0.025)
#sd1
sd1 <- (upper1-mean1)/qnorm(0.975)
sd1
# 2. 10000 random draws from normal. but we have a truncated normal 
# do not use rtrunc (there is a hint that this procedure is not fully correct)
# set seed to produce exactly reproducable random numbers
set.seed(1)
#pargkmDE <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
pargkmDE <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
meangkmDE <- mean(pargkmDE)
meangkmDE
# plot distribution
## sequence of 1000 values between lower and upper bounds
xgkm <- seq(from=lower1, to = upper1, by=0.01)


## plot density and histogram
hist(pargkmDE, breaks=80, main="", xlab="gkmDE - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygkm <- dtruncnorm(xgkm, a=lower1, b=upper1, mean=mean1, sd=sd1) * (numberrandom*0.05)
lines(xgkm,ygkm)
png("imggkmDE.png")
hist(pargkmDE, breaks=80, main="", xlab="gkmDE - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygkm <- dtruncnorm(xgkm, a=lower1, b=upper1, mean=mean1, sd=sd1) * (numberrandom*0.05)
lines(xgkm,ygkm)
dev.off()
```


### 3.1.2 pargkmUS

pargkmUS $\equiv$  avg. private travel cost per km by car () in the U.S.

**Use truncated normal distribution** 

* \citet{CompostellaEtAl2020} provide survey and own calculations. We use their 
own calculations because they improve on the literature. 
* 68 conventional (CV) and autonomous cars (AV) (including ride sharing) ($N=68$). 
Small and medium sized cars in 2020 and in 2030. 
* Their numbers in VMT. We use them in VKT and EUR ((mile -> 1.60934 km; 
1 US-$ = 0.84 EUR at March 19, 2021); 

* Assumptions: current prices. data for near-term cars (Fig. 2); lowest 50 US-ct 
(Private ICEV in 2020 - Small SUV, lower limit) and highest 2.35 US-ct 
(Ridesource, upper limit) are borders of the symmetric 95% confidence intercal CI
* lower1 is used as 95% quartil, $\mu =1/2 * (0.50+2.35)$   $$\rightarrow sd = 
\text{lowerlimit})/1.96$$ 
* 10000 (numberrandom) draws from the truncated normal distribution with support 
lowerlimit and upperlimit


```{r gkmUS}
lower1 <- 0.50*EURDollar/kmmile
lower1
upper1 <- 2.35*EURDollar/kmmile
upper1
mean1 <-1/2 * (lower1 + upper1)
mean1
#lower1 2.5% percentile of a normal distribution
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws
## random draws
set.seed(1)
pargkmUS <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
meandgkmUS <- mean(pargkmUS)
meandgkmUS
# plot distribution
## sequence of 1000 values between lower and upper bounds
xgkm <- seq(from=lower1, to = upper1, by=0.01)
xgkm
## vector of values of the heigth of the probability distribution for each value of x 
xgkm <- seq(from=lower1, to = upper1, by=0.01)

## plot density and histogram
hist(pargkmUS, breaks=80, main="", xlab="pargkmUS - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygkm <- dtruncnorm(xgkm, a=lower1, b=upper1, mean=mean1, sd=sd1)*1000
lines(xgkm,ygkm)
png("imggkmUS.png")
hist(pargkmUS, breaks=80, main="", xlab="pargkmUS - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygkm <- dtruncnorm(xgkm, a=lower1, b=upper1, mean=mean1, sd=sd1)*1000
lines(xgkm,ygkm)
dev.off()
```

## 3.2 gx (variable monetary costs of VKT during in-vehicle work)

### 3.2.1 pargsDE

Variable monetary costs of VKT for firms. 

**Assumptions**

* Use only AV that are electric cars
* variable costs $=$ electriciy costs
* energy consumption: 18 kWh/100 km \citep{Deloitte2019}
* \citet{ADAC2020b} 5.53 EUR-ct/km (operating costs of 830EUR/anno divided by 
15.000 km/anno) (upperlimit) and 3.8 EUR-ct/km (lowerimit) if charged at the 
firm (the latter at lower commercial electricity costs. Small firms up to 50000 
kWh/anno pay 21.19 EUR-ct per kWh \href{https://strom-report.de/strompreis-gewerbe/}). 
Private households pay on average 27.38 (source?)

```{r, gxDE}
lower1 <- 0.038
lower1
upper1 <- 0.0553
upper1
# 2. 10000 random draws from a uniform distribution
set.seed(12)
pargsDE <- runif(numberrandom, min = lower1, max=upper1)
meangsDE <- mean(pargsDE)
meangsDE
```

### 3.2.2 pargsUS

Variable monetary costs of VKT for firms in the U.S.

**Assumptions**

* only fuel costs of ridesource vehicles in 2030-35 (VKT of commercial cars > 
VKT of private cars)
* \citet{CompostellaEtAl2020}: N=6 (t-distribution; 5 dgf) 0.03 \$/VMT (lowerlimit), 
0.09 \$/VMT (only fuel cost USD/VMT)

```{r, pargsUS}
kmmile <- 1.06934
EURDollar <- 0.84
lower1 <- 0.03*EURDollar/kmmile
lower1
upper1 <- 0.09*EURDollar/kmmile
upper1
# We use a uniform distribution of energy/fuel cost per km
# 2. 10000 random draws from uniform distribution with support lower1 and
set.seed(12)
#pargsUS <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
pargsUS <- runif(numberrandom, min = lower1, max=upper1)
meandgsUS <- mean(pargsUS)
meandgsUS
```

## 3.3 gd (average fixed monetary costs of travel per hour of invehicle work (EUR$/v$))

### 3.3.1 pargdDE

Fixed monetary travel costs per hour of in-vehicle work (calculations: 171.83 EUR/month 
BMW i3's fixed costs per month from \citet{ADAC2020b} that include insurance, taxes, 
maintenance costs. Add monthly leasing rate 180 EUR/month. Sum is aggregate fixed 
costs per month. If the car is used 19 workdays per month á 12 hours per day we get 
1.54 EUR/h).  Result: 1.54 EUR/h.

We assume a uniform distribution between 1.04 EUR/h and 7 EUR/h due to leasing rates 
for 30000 km/a including environmental subsidy (Umweltbonus, 5000€). The only 
information we have are both limits.   \citep{CompostellaEtAl2020}. (Leasing costs 
are currently between 50 EUR/month and 354 EUR/month.) The car is fully leased by 
the firm, while \citet{CompostellaEtAl2020} assumes that the car is rented per km 
(like a driverless taxi).  {\color{blue} To be checked } Following an announcement 
of VW that leasing will be 7 EUR/h, we use this is upper limit.

```{r, pargdDE}
set.seed(123)
pargdDE <- runif(numberrandom, 1.04, 7)
meangdDE <- mean(pargdDE)
meangdDE
```

### 3.3.2 pargdUS


* \citet{CompostellaEtAl2020}: 80,000 mileage per year, lower limit 0.33 \$/VMT, 
upper limit: 0.37 \$/VMT. (Tab A3/A4, used total USD/VMT minus fuel costs for car 
offered by the employer: ridesource)
* We assume: 53 weeks $\rightarrow$ 106 free days, plus 4 to consider additional 
holidays of the firm (Christmas, labor day) $=$ 110. Hence travel days = $365-110$, 
usage of AV: 12 hours per day

```{r, pargdUS}
traveldays <- 365-110
hoursday <- 12
mianno <- 80000
costannolow <- mianno*0.33/(traveldays*hoursday)*EURDollar
costannolow
costannoupp <- mianno*0.37/(traveldays*hoursday)*EURDollar
costannoupp
lower1 <- costannolow
lower1
upper1 <- costannoupp
upper1
mean1 <-1/2 * (lower1 + upper1)
mean1
# lower1 defines the 2.5% percentile of a normal distribution
sd1 <- (upper1-mean1)/qnorm(0.975)
sd1
# 2. 10000 random draws from truncated normal distribution
set.seed(123)
pargdUS <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
meangdUS <- mean(pargdUS)
meangdUS
## sequence of 500 values between lower and upper bounds
xgh <- seq(from=lower1, to=upper1, by=0.001)
hist(pargdUS, breaks=40, main="", xlab="pargdUS - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygh <- dtruncnorm(xgh, a = lower1, b=upper1, mean = mean1, sd =sd1) * (numberrandom*0.05)
lines(xgh,ygh)
## histogram and density
png("imggdUS.png")
hist(pargdUS, breaks=40, main="", xlab="pargdUS - random numbers from a truncated normal")
# multiply N with bin width 0.1 of the histogram
ygh <- dtruncnorm(xgh, a = lower1, b=upper1, mean = mean1, sd =sd1) * (numberrandom*0.05)
lines(xgh,ygh)
```



Further

## 3.4 Two-way Commuting Distance 

* distance (two-way commuting distance)


### 3.4.1 Commuting distance Germany (distanceDE)

First estimate: \citet{DauthHaller2018}: 21 km (two-way). 9.6\% commute between 0-2 km. 
We approximate the histogram provided by \citep{DauthHaller2018}.

\begin{figure}[htb]
\includegraphics{./Graphics/DauthHaller2018_PendeldistanzVerteilung}
\caption{Commuting distance in Germany} \label{fig: CommuteDistDE}
\end{figure}

```{r message=FALSE, warning=FALSE}
# calculate gamma distribution for commuting distance (one-way)
distlowerDE <- 2
distmeanDE <- 10.5
distupperDE <- 90
# interval [lower,upper] whith borders at plower% and pupper% quantile and mean 
# with non linear maximization
# calculate distribution for plower, mean as 70%-percentil, pupper 
p <- c(0.076,0.7,0.995)
# calculate distribution 
## p=c(2,0.1) are start values for shape and rate
## draw vertical lines at p
solution <- nlm(f=errorGamma, p=c(2,0.1), quantiles=p, 
                exp=c(distlowerDE, distmeanDE, distupperDE),print.level=0);
shape.distDE <- solution$estimate[1]
rate.distDE  <- solution$estimate[2]
#plotGamma(shape.elastM0I, rate.elastM0I[,1], p=p)
plotGamma(shape.distDE, rate.distDE, p=p)
# use one-way distance Gamma-distribution for random draws of two-way distances
set.seed(1234)
distanceDE <- rgamma(numberrandom,shape.distDE,rate.distDE)
distanceDE <- 2*distanceDE
meanddistDE <- mean(distanceDE)
meanddistDE
# plot histogram
hist(distanceDE, breaks=80, main="", xlab="distanceDE - random numbers from a gamma")
png("imgdistanceDE.png")
hist(distanceDE, breaks=80, main="", xlab="distanceDE - random numbers from a gamma")
```


### 3.4.2 Commuting distance US (distanceUS)

\begin{table}[htb]
\centering
\begin{tabular}{l|c}
\hline
\hline
  Commute distance (miles) 2003 & Percent \\
  \hline
  1-5   & 29 \\
  6-10  & 22 \\
  11-15 & 17 \\
  16-20 & 10 \\
  21-25 & 7 \\
  26-30 & 5 \\
  30-34 & 3  \\
  $\geq$ 35 & 8 \\
  \multicolumn{2}{l}{\cite{BTSt2003}, Quick Facts} \\
  \hline
  \multicolumn{2}{l}{Stretch commute $\geq$ 59 miles}\\
  35-49 & 5.3 \\
  $\geq$ 50 & 2.7 \\
  $\geq$ 200 & 0.16 \\
  \hline
  \multicolumn{2}{l}{\cite{BTS2017}}
  \end{tabular}
  \caption{Commuting distance: 2003} \label{tab: DistWorkUS2003}
\end{table}

```{r message=FALSE, warning=FALSE}
# one-way commuting
# 3.3 millions employees from about 121 in the U.S. stretch commute 
# (travel more than 50 miles one way) (BTS, 2017). This is one-way distance.
sharestretch <- 3.3/121
# From these 2.7% of all commuters share of of travel distances are: 
# 22% 50-74 miles, 19% 75-99 miles, 7% 100-124, 6% 125-199, 6% 200+ (BTS, 2017)
share200 <- 0.06*sharestretch
# 6% of those commute more than 200 miles almost each day 
# calculate gamma distribution for commuting distance (one-way)
distlowerUS <- 5*kmmile
# mean 25.75 km (16 miles)
distmeanUS <- 15.3*kmmile
distmedianUS <- 10*kmmile
distupperUS <- 200*kmmile
distmeanUS
distlowerUS
distupperUS
#percent lower and upper (share of lowest and highest distance interval in the data)
plower <- 29/100
plower
pupper <- 1-share200
pupper
# interval [lower,upper] whith borders at plower% and pupper% percentile and mean 
# with non linear maximization
# calculate distribution for plower, mean as 74,5%-percentil, pupper 
p <- c(plower,0.748,pupper)
# calculate distribution for plower, mean as 50%, pupper 
#p <- c(0.001,0.5,0.9984)
# calculate distribution 
## p=c(2,0.1) are start values for shape and rate
## draw vertical lines at p
solution <- nlm(f=errorGamma, p=c(2,0.1), quantiles=p, 
                exp=c(distlowerUS, distmeanUS, distupperUS),print.level=0);
shape.distUS <- solution$estimate[1]
rate.distUS  <- solution$estimate[2]
plotGamma(shape.distUS, rate.distUS, p=p)
# use Gamma-distribution for random draws (two-way, drawn from one-way)
set.seed(1234)
distanceUS2 <- rgamma(numberrandom,shape.distUS,rate.distUS)
# two-way distance
distanceUS <- 2*distanceUS2
meandistUS <- mean(distanceUS)
meandistUS
mediandistUS <- median(distanceUS)
mediandistUS
# mean should be 30.6
## plot histogramn 
hist(distanceUS, breaks=80,main="", xlab="distanceUS - random numbers from a gamma")
png("imgdistanceUS.png")
hist(distanceUS, breaks=80,main="", xlab="distanceUS - random numbers from a gamma")


```


## 3.5 Two-way Commuting Time 

### 3.5.1 Commuting time Germany (avgTimeDE)

\begin{table}[htb]
  \centering
  \begin{tabular}{l|c|c}
  \hline
  \hline
  One-Way Commute time min & Percent \\
  $\leq$ 15 & 19  \\
  15-29     & 31 \\
  30-59     & 20 \\
  60-119    & 5  \\
  $\geq$ 120  & 1 \\
  no commut & 24 \\
  \hline
  \multicolumn{2}{l}{Source: Survey conducted by \citep{Statista2021a}, $N=$2099, 
  age: 18-64}
  \end{tabular}
  \caption{Daily one-way commuting time DE, 2020} \label{tab: commutetimeDE}
\end{table}

Average commuting time in Germany in 2010 is 44 minutes two way. \citet{GimenezNadal2020}

```{r message=FALSE, warning=FALSE}
# two way
avgTimeDE <- 44
# calculate gamma distribution for one-way commuting distance
timelowerDE <- 15
timemeanDE <- 22
timeupperDE <- 120
#percent lower and upper in the table (76% of workforce is commuting)
plower <- 19/76
plower
pupper <- 1-1/76
pupper
# interval [lower,upper] with borders at plower% and pupper% percentile and mean 
# with non linear maximization
# calculate distribtion for plower, mean as 72.2\% percentile to achieve avgtimeDE, pupper 
p <- c(plower,0.7236,pupper)
# calculate distribution parameters shape and rate
## p=c(2,0.1) are start values for shape and rate, draw vertical lines at p
solution <- nlm(f=errorGamma, p=c(2,0.1), quantiles=p, 
                exp=c(timelowerDE, timemeanDE, timeupperDE),print.level=0);
shape.timeDE <- solution$estimate[1]
rate.timeDE  <- solution$estimate[2]
plotGamma(shape.timeDE, rate.timeDE, p=p)
# use Gamma-distribution for random draws (two way from distribution for one way)
set.seed(3)
timeDE <- rgamma(numberrandom,shape.timeDE,rate.timeDE);
timeDE <- 2*timeDE
meantimeDE <- mean(timeDE)
meantimeDE
# plot histogram
hist(timeDE, breaks=80, main="", xlab="timeDE - random numbers from a gamma")
png("imgtimeDE.png")
hist(timeDE, breaks=80, main="", xlab="timeDE - random numbers from a gamma")


```


### 3.5.2 Commuting time US (avgTimeUS)

First estimate: Average one-way commuting time is 27.6 minutes in 2020 (54.2 two-way). 
9.8\% commute at least one hour (one-way!) \citep{USDepTr2020}


\begin{table}[htb]
\centering
\begin{tabular}{l|c}
\hline
\hline
Travel time (min) & Percent \\
\hline
  $\leq$ 5  & 2.7 \\
  5-9   & 9.2 \\
  10-14 & 12.9 \\
  15-19 & 14.9 \\
  20-24 & 14.1 \\
  25-29 & 6.6 \\
  30-34 & 13.9 \\
  35-39 & 3.2 \\
  40-44 & 4.1 \\
  45-59 & 8.5 \\
  60-89 & 6.7 \\
  $\geq$ 90 & 3.1 \\
  \hline
    \cite{BurdEtAl2021}, Table 1, p.3 \\
  \hline
  \end{tabular}
  \caption{Travel Time To Work: 2019} \label{tab: TTWorkUS2019}
\end{table}


```{r message=FALSE, warning=FALSE}
# two-way 
avgTimeUS <- 54.2

# calculate gamma distribution for one-way commuting distance
timelowerUS <- 5
timemeanUS <- 27.6
timeupperUS <- 89
# interval [lower,upper] whith borders at plower% and pupper% percentile and mean 
# with non linear maximizati
# use low as plower, mean as 65.2% to achieve avgTimeUS, and pupper 
p <- c(0.027,0.652,0.969)
# p=c(2,0.1) are start values for shape and rate
# draw vertical lines at p
solution <- nlm(f=errorGamma, p=c(2,0.1), quantiles=p, 
                exp=c(timelowerUS, timemeanUS, timeupperUS),print.level=0)
shape.timeUS <- solution$estimate[1]
rate.timeUS  <- solution$estimate[2]
plotGamma(shape.timeUS, rate.timeUS, p=p)
# use Gamma-distribution for random draws
set.seed(3)
timeUS <- 2*rgamma(numberrandom,shape.timeUS,rate.timeUS)
meantimeUS <- mean(timeUS)
meantimeUS
# plot histogram
hist(timeUS, breaks=80, main="", xlab="timeUS - random numbers from a gamma")
png("imgtimeUS.png")
hist(timeUS, breaks=80, main="", xlab="timeUS - random numbers from a gamma")

```


### 3.5.3 Average Speed in German Cities (tkmDE)

Average speed in German cities in 2018 \citep{Statista2020}

*  11mph: Berlin, Munich, Frankfurt, Leipzig, Bonn
*  12mph: Hamburg, Bremen, Karlsruhe, Augsburg
*  13mph: Köln, Stuttgart, Nürnberg, Hannover, Wiesbaden
*  14mph: Düsseldorf, Wuppertal, Mannheim 

SRV for Berlin: average trip with car on a normal day in 2018 is 22.3 min, 7.4 km, 
19.8 km/h \citep{GerikeEtAl2020}. However, this is average speed. Since commuting 
is mainly occurring during peak hours, speed is lower. We use the speed provided 
by \citep{Statista2020} which is 17.7 km/h (11 mph).

There is a correlation between commute time and commute distance. It is about 0.78 
in the NL in the 1990s (Rietveld et al. 1999). Hence we cannot independently choose 
time per km and distance. We draw distances from above (MC). Then we calculate for 
each draw of distance the corresponding average travel time per km by applying the 
approach of \citet{Rietveld1999}. 

Average speed is avgtime/avgdistance. Shorter distances takes longer time 
(speed is 0.6/1 times slower than for distance beyond 25km) \citep{Rietveld1999}. 

We use the following information: average speed in large cities, average distance 
of all commutes (22 km one-way = mean). Distance below are usually traveled at 
lower speed \citep{Rietveld1999}.  According to \citet{Rietveld1999}, travel 
speed increases considerably with distance mainly due to high costs for the first 
km and the increasing share of highways used at longer commutes.    

```{r, tkmDE}
# speed in km/h
speed11 <- kmmile*11
speed12 <- kmmile*12
speed13 <- kmmile*13
speed14 <- kmmile*14
speed18 <- kmmile*18
speed11
speed12
speed18
# for each random draw of distanceDE (tx), draw tkmDE (travel time per km).
# distribution of speed below 25 km depends on speed11--speed14. Use one-way distance 
#instead of two-way distance. 
# Example: Berlin
# avg. distance of a car trip in Berlin, 2018 = 7.4 km
distcities <- 7.4
#Since distance is 7.4km on average in Berlin, we use the 
#first part of the kinked-linear regression line from \citet{Rietveld1999} and calculate 
#parameters to meet the city-specific time and speed. This holds for all other 
# 11mph-cities.
# Speed within city of Berlin (speed11): Travel time of avg. distanced trip 7.4km 
# with average commuting speed in minutes
time11 <- distcities/speed11*60
time11
time18 <- distcities/speed18*60
time18
# set parameters of kinked travel time function time = f(distance): 
# For distances below 25km: time = a + b*dist
# We fix a = 8 (about the parameter estimated by Rietveld et al. (1999) for NL). 
# Solve for b :  b = (time-a)/dist = (1/speed*60 - a)/dist
# b calculated for one-way trips
parb11 = (time11-8)/distcities
parb11
parb18 = (time18-8)/distcities
parb18
# As a consequence: travel time in Berlin for a trip of length 2 km = 12.6 min, 
#7.4 km = 25.1 min, 25 km = 65.7 min


# 11 mph for most congested A-cities, B-cities, C-cities: B, F, M; BN, L; Augsburg
# 14 mph for less congested A-city: D; 7th cong. B-city: Mannheim; 2nd congested 
# C-city: Wuppertal
# 18 mph assumed for fastest B- and C-cities.

# Parameter c from Rietveld et al. (1999) = 0.6
# draw from a uniform distribution
# calculate travel time for each distance traveled in minutes
# calculate travel time per km in hours (for distances below 0.1 km we have fixed time of 8 minutes)
set.seed(31)
parambDE <- runif(numberrandom,min=parb18, max=parb11)
timedistDE <- c(1:10000)
timekmDE <- c(10000)
summary(distanceDE)
for(i in 1:numberrandom) {
  timedistDE[i] <- 8 + parambDE[i] * min(distanceDE[i]/2,25) + 0.6 * 
    max(distanceDE[i]/2-25,0)
  if (distanceDE[i]>=0.1) {
    timekmDE[i] <- (timedistDE[i]*60/distanceDE[i])/360
  }
  else
   { timekmDE[i] <- (timedistDE[i]*60)/360
   }
}
timedistDE <- timedistDE*2;
meantimekmDE <- mean(timekmDE)
meantimekmDE
#timekmDE
min(timekmDE)
max(timekmDE)
```





### 3.5.4 Average Speed in US-Cities  (tkmUS)

First estimate: Average speed according to \citet{Geotab2018}, average rush-hour 
speed in major U.S. cities range from 19 mph in Washington D.C. to 41 mph in St. Louis. 


```{r message=FALSE, warning=FALSE}
speed19 <- kmmile*19
speed41 <- kmmile*41
# average travel time US-cities in min:  22.6 (city <- 30000) - 33.1 (>= 5 Mill)
time19 = 33.1
time41 = 22.6
# calculate avg dist
distcit19 <- speed19 * time19 / 60
distcit41 <- speed41 * time41 / 60
# set parameters of kinked travel time function time = f(distance): 
# For distances below 25km: time = a + b*dist
# We fix a = 8 (about the parameter estimated by Rietveld et al. (1999) for NL). 
# Solve for b :  b = (time-a)/dist = (1/speed*60 - a)/dist
# b calculated for one-way trips
parb19 = (time19-8)/distcit19
parb19
parb41 = (time41-8)/distcit41
parb41

# Parameter c from Rietveld et al. (1999) = 0.6
# draw from a uniform distribution
# calculate travel time for each distance traveled in minutes
# calculate travel time per km in hours (for distances below 0.1 km we have fixed time of 8 minutes)
set.seed(31)
parambUS <- runif(numberrandom,min=parb41, max=parb19)
timedistUS <- c(1:10000)
timekmUS <- c(10000)
summary(distanceUS)
for(i in 1:numberrandom) {
  timedistUS[i] <- 8 + parambUS[i] * min(distanceUS[i]/2,25) + 0.6 * 
    max(distanceUS[i]/2-25,0)
  if (distanceUS[i]>=0.1) {
    timekmUS[i] <- (timedistUS[i]*60/distanceUS[i])/360
  }
  else
   { timekmUS[i] <- (timedistUS[i]*60)/360
   }
}
timedistUS <- timedistUS*2;
meantimekmUS <- mean(timekmUS)
meantimekmUS
#timekmDE
min(timekmUS)
max(timekmUS)



```








## 3.6 Avg. hours per workday

### 3.6.1 Avg. hours per workday Germany

Full-time equivalents
* 8 hours day
* 33 hours paid leave days \citep{Maye2019}
* 251 workdays in 2019 (minus weekends)
* 251-33 = 218 workdays / 12 month = 18.2 workdays per month


### 3.6.2 Avg. hours per workday US

* 7.62 h/day (U.S. Bureau of Labor Statistics; \href{https://www.bls.gov/data/}{BLS})
* 251 workdays in 2019
* US 10 paid leave days and 6 holidays on average \citet{Maye2019}
* 235 workdays per year / 12 = 19.58 workdays per month


# 3.7 Productivity

Per labor hour (all workers, not only FTEs)

## 3.7.1 Productivity Germany

  * Annual hours worked per worker in 2019: DE 1386 h/year (OECD 2021: \href{https://stats.oecd.org/Index.aspx?DataSetCode=ANHRS} (accessed on 22 March 2021)
 *  Employment DE 2019: 41061 k (OECD 2021: \href{https://stats.oecd.org/Index.aspx?DataSetCode=LFS_D} 
 (accessed on 22 March 2021)
 * GDP DE 2019: 4644164 million \$ \href{https://doi.org/10.1787/dc2f7aec-en} 
 (accessed on 22 March 2021) 
 * Avg. prod per hour worked (own calculation)
 * GDP per hour worked: own calculations:
 
```{r, GDPperHourDE}
# GDP in 2019 in $/year
GDPDE <- 4644164000000*EURDollar
# Avg. hours worked per worker and year (h/year) in 2019
HoursYearDE <- 1386
# Number of employees US in 2019
EmployeesDE <- 41061000
avgprodDE1 <- GDPDE/(HoursYearDE*EmployeesDE)
set.seed(314)
avgprodDE <- runif(numberrandom, min = avgprodDE1, max = avgprodDE1)
meanavgprodDE <- mean(avgprodDE)
meanavgprodDE
``` 

## 3.7.2 Productivity U.S.

 (U.S. Bureau of Labor Statistics; \href{https://www.bls.gov/data/}{BLS})
 
 GDP per hour worked: 
 \href{https://ourworldindata.org/grapher/labor-productivity-per-hour-pennworldtable?tab=table}{Our World in data}
 
 * Annual hours worked per worker in 2019: US 1779 h/year (OECD 2021: \href{https://stats.oecd.org/Index.aspx?DataSetCode=ANHRS} (accessed on 22 March 2021)
 * Employment U.S.\ in 2019 147194 k (OECD 2021: 
 \href{https://stats.oecd.org/Index.aspx?DataSetCode=LFS_D}) (accessed on 22 March 2021)
 * OECD (2021), Gross domestic product (GDP) (indicator). U.S. 2019: 21433226 million \$ \href{https://doi.org/10.1787/dc2f7aec-en} (accessed on 22 March 2021)
 * Avg. prod per hour worked (own calculation)
 
GDP per hour worked is
```{r, GDPperHourUS}
# GDP in 2019 in $/year
GDPUS <- 21433226000000*EURDollar
# Avg. hours worked per worker and year (h/year) in 2019
HoursYearUS <- 1779
# Number of employees US in 2019
EmployeesUS <- 147194000
avgprodUS1 <- GDPUS/(HoursYearUS*EmployeesUS)
avgprodUS1
set.seed(314)
avgprodUS <- runif(numberrandom, min = avgprodUS1, max = avgprodUS1)

```


# 3.8 AVG: Wage

Only Full-time-equivalent employees (FTE)

## 3.8.1 Avg. wage and wage distribution Germany


* Average annual gross wage per worker DE: (current prices, OECD)  42421 EUR {\href{https://stats.oecd.org/Index.aspx?DataSetCode=LFS_D}, (accessed on 22 March 2021)}
* Avg. gross wage/h per FTE (full-time equivalent) worker in different sectors in 
Germany, 2019 (see \ref{tab: wageDE1})
* skilled-dependent avg.\ gross wage/h per FTE in Germany, 2018 (see \ref{tab: wageDE})
* Minimum wage in 2019: 9.50 EUR/h \citet{DeStatis2021}
* wage distribution in Germany, 2018 \citet{DeStatis2018}
* Graphic below: own graph based on data from table 1.1.4 in \citet{DeStatis2018}. Wages of full time workers, in Agriculture, Manufacturing, and Services. 

\begin{figure}[htb]
\includegraphics{./Graphics/HourlyWagesDE2018}
\caption{Hourly wages for FTE in Germany, 2018} \label{fig: wagesDE}
\end{figure}



```{r warning=FALSE, message=FALSE}
# Estimate kernel density of the German gross wage distribution 
#(thanks to F. Javier Rubio: Kernel Density and Distribution Estimation for data 
# with different supports, 11 August, 2017)

# Data from \citet{DeStatis2018}, Tab 1.1.4
datawageDE <- read.table("WagesHistogramDestatis2018FSTab114.csv", sep = ";", header = TRUE)

library(kerdiest)

datawageDE2.data <- c(runif(datawageDE[1,2],datawageDE[1,3]-0.4,datawageDE[1,3]+0.4))
for (n1 in 2:135) {
  datawageDE2.data <- c(datawageDE2.data,
                            c(runif(datawageDE[n1,2],datawageDE[n1,3]-0.4,datawageDE[n1,3]+0.4)))
}
# calculate bandwith
# x quantiles
# h,b0 smoothing, bandwith
kde.dunif <- function(x,h,data) mean( dunif(x-data,0,h))

b0 <- bw.nrd0(datawageDE2.data)
b0
kde.dfit <- Vectorize(function(x) kde.dunif(x,b0,datawageDE2.data))
hist(datawageDE2.data,probability = T, breaks = 135, ylim = c(0,0.06), xlab = "gross wage", ylab = "Density", main="Histogram vs KDE")
curve(kde.dfit,0,140,lwd=3,col="blue",add=T,n=50)
box()
ww <- kde.dunif(100,b0,datawageDE2.data)

# 10000 random draws from the kernel density
wagehist <- hist(datawageDE2.data,breaks=135,freq=FALSE)
set.seed(17)
samplesize = 10000
bins=with(wagehist,sample(length(mids),samplesize,p=density,replace=TRUE)) 
# choose a bin
wageDE =runif(length(bins),wagehist$breaks[bins],wagehist$breaks[bins+1]) 
# sample a uniform in it
hist(wageDE,probability = T, breaks = 100, ylim = c(0,0.06), xlab = "gross wage", ylab = "Density", main="Random draws of wage DE")

```


 




## 3.8.2 Avg wage and wage distribution US



\begin{table}[htb]
  \begin{tabular}{l|c|c}
   \hline \hline 
    \multicolumn{3}{c}{Average hourly wage of FTE in 2019$^\text{a}$} \\
    \hline
    Occuption & wage \$/h & rel. s.e.\\
    Full-time business/financ operations occuption Bloomington, IN & 31.53 & 1.5 \\
    Full-time business/financ operations occuption (U.S.) & 37.65 & -- \\
    Level 06 management occup (U.S.) & 16.31 & -- \\
    Level 06 accountants and auditors (U.S.) & 24.88 & 2.5 \\
    Level 09 accountants and auditors (U.S.) & 36.87 & 2.8 \\
    Level 12 accountants and auditors (U.S.) & 69.98 & 12.8 \\
    Level 06 computer/math occup. Austin-Round Rock, TX & 22.67 & 5.7 \\
    Level 08 computer/math occup. Austin-Round Rock, TX & 32.54 & 2.8 \\
    Level 11 computer/math occup. Austin-Round Rock, TX & 51.78 & 1.8 \\
    Avg. worker (U.S. - average; Q4) & 25.72$^\text{b}$ & 1.1 \\
    Compensation (soc. benefits; Q4) & 11.03 & 1.5 \\
    \hline
    \multicolumn{3}{l}{\footnotesize $^{\text{a}}$ \citet{USBoL2021a}} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{b}}$ \citet{USBoL2021a}}
  \end{tabular}
  \caption{Average hourly wage in office jobs,U.S.\ 2019} \label{eq: wageUS}
\end{table}

\begin{table}[htb]
  \begin{tabular}{l|c|c}
   \hline \hline 
    \multicolumn{3}{c}{Median weekly wage of FTE workers in 2019, U.S.} \\
    \hline
    Education & \$/week & \\
    \hline 
    High school graduates, no college & 747 & \\
    Bachelor's degree or higher & 1382 &  \\
    Bachelor's degree only & 1259 & \\
    Advanced degree & 1571 & \\
    \hline
    \multicolumn{3}{l}{\footnotesize \citet{USBoL2021a}} \\
     \multicolumn{3}{l}{\footnotesize 25 years and over } \\         
     \multicolumn{3}{l}{\footnotesize State and county, avg. wages all workers 
     are available} \\
     \multicolumn{3}{l}{\footnotesize Avg.\ hours worked, business/financ.\ 
     services = 34.4 h/week}
  \end{tabular}
  \caption{Average hourly wage in office jobs, 2019} \label{tab: AvgwageeducationUS}
\end{table}

Wage distribution in the U.S.

* Average annual wage per worker U.S.: 65836 USD  
  \citet[current prices, 2020][]{OECD2021}  $\rightarrow$ used for calculating 
  the average wage
* Avg. hourly wage for some occupation groups, FTE U.S., 2019/4 (see \ref{eq: wageUS})
* Avg. hourly wage according to education level, FTE U.S., 2019/4 
  (see \ref{tab: AvgwageeducationUS})
* minimum wage in 2019: 7.25 USD/h \citet[see][]{USDoL2021}

We use Table \ref{eq: wageUS} for low and high wages (used as percentiles)

Data on the wage distribution see also \citet{Gould2020}.

\begin{table}[htb]
  \centering
  \begin{tabular}{r|c}
    \hline
    \hline
    Percentile & USD/h \\
    \hline
    10 & 10.07 \\
    20 & 12.31 \\
    30 & 14.64 \\
    40 & 16.71 \\
    50 & 19.33 \\
    60 & 22.95 \\
    70 & 27.94 \\
    80 & 34.98 \\
    90 & 48.08 \\
    95 & 67.14 \\
  \hline
  \multicolumn{2}{l}{\footnotesize Source: \citep{Gould2020}} \\
  \multicolumn{2}{l}{\footnotesize Avgl.\ wages per percentiles in 2019 in 2019}. \\
  \hline
  \end{tabular}
  \caption{Wages US, 2019} \label{tab: WagesUS}
\end{table}

```{r message=FALSE, warning=FALSE}
# calculate gamma distribution for avg, wage
wagelowerUS  <- 10.07*EURDollar
wageupperUS <- 67.14*EURDollar
wageminimumUS <- 7.25*EURDollar
# OECD annual avg. wage / avg. work hours per year: 
wagemeanUS <- 25.72
wagemeanUS
wagelowerUS
wageupperUS
# 65836/HoursYearUS*EURDollar
# interval [wagelower,wageupper] whith borders at 10% and 95% percentile 
# and mean 0.66 (25.72 is between 60th and 70th percentile)
# with non linear maximization
# use wagelower as 5%, wagemean as 57.6193%, and wageupper as 95% 
p <- c(0.10,0.576193,0.95)
# p=c(2,0.1) are start values for shape and rate
solution <- nlm(f=errorGamma, p=c(2,0.1), quantiles=p, 
                exp=c(wagelowerUS, wagemeanUS, wageupperUS),print.level=0)
shape.wageUS <- solution$estimate[1]
rate.wageUS  <- solution$estimate[2]
plotGamma(shape.wageUS, rate.wageUS, p=p)
# use Gamma-distribution for random draws
set.seed(321)
wageUS <- rgamma(numberrandom,shape.wageUS,rate.wageUS)
meanwageUS <- mean(wageUS)
meanwageUS
# plot histogram
hist(wageUS, breaks=60, main="", xlab="wageUS - random numbers from a truncated normal")
png("imgwageUS.png")
hist(wageUS, breaks=60, main="", xlab="wageUS - random numbers from a truncated normal")

```
# 3.9 AVG wage tax rate (including social security payments)

Only Full-time-equivalent employees (FTE)

## 3.9.1 Avg. wage and social security rates on gross-wages Germany

\citet{OECD2020}

* single earner (Avg. income), 42651 USD annual taxable income (gross wage minus employers social insurance contributions). 10037 USD income tax, 10476 USD soc security contributions = 20514 USD payments to government
* family with 2 children: 
** 1 earner with avg. wage, 42746 USD, 786 USD income tax, 19346 USD soc sec.
** 2 earner with 100\% and 67\% income: 55863 USD taxable income, 9807 USD income tax, 17277 USD soc sec. = 27084 USD payments to government

``` {r avg wage tax rate}
# Simply calculate average of a single earner with avg wage and a family with two earners, one earning avg. wage the other 2/3 of avg. wage
wageEURDE = 0.5*(55863 + 42561)*EURDollar
wageEURDE
taxliabilityDE = 0.5 * (20514+27084)*EURDollar
taxliabilityDE
avgtaxrateDE = taxliabilityDE/wageEURDE
avgtaxrateDE

```

## 3.9.2 Avg. wage and social security rates on gross-wages U.S.



\citet{OECD2020}

* single earner (Avg. income), 57055 USD annual taxable income (gross wage minus employers social insurance contributions). 5727 USD income tax, 3608 states and local taxes, 4365 USD soc security contributions = 13699 USD payments to government
* family with 2 children: 
** 2 earner with 100\% and 67\% income: 95282 USD taxable income, 4118 USD income tax, 5590 state and local taxes, 7289 USD soc sec. = 16997 USD payments to government

``` {r avg wage tax rate US}
# Simply calculate average of a single earner with avg wage and a family with two earners, one earning avg. wage the other 2/3 of avg. wage
wageEURUS = 0.5*(57055 + 95282)*EURDollar
wageEURUS
taxliabilityUS = 0.5 * (13699+16997)*EURDollar
taxliabilityUS
avgtaxrateUS = taxliabilityUS/wageEURUS
avgtaxrateUS

```



# 4. Office Parameters

## 4.1. Monthly rent per sqm of office space

### 4.1.1 Germany (rmonthDE)

In Germany, data on office rents are not publicly available. There is a small 
number of statistics aoffered by private firms (see Table \ref{tab: officerentsDE}). 
Nothing is known about the distribution of officen rents. We assume, that rents 
span equally between the lowest rent and highest rent in the seven largest cities 
(Big 7). Of course, intuitively there is less office space in the upper segment.


\begin{table}[htbp]
  \centering
  \begin{tabular}{l|c|c|c|c|c|c}
    \hline \hline
    \multicolumn{7}{c}{Rents office space 2019-2020 [EUR/m$^2$]} \\
    \hline
    City            & average  & max.       & lowest     & avg.add.  & available 
    & newly rented \\
                    & EUR/qm   & EUR/qm     & EUR/qm     & costs sqm & mill.sqm  
                    & mill.sqm      \\
    \hline
    Berlin          & 28.70$^{\text{c}}$ & 38,00$^{\text{k}}$ & 9.00$^{\text{k}}$  & 3.68$^{\text{m}}$ 
                    & 20.80$^{\text{k}}$ & 0.999$^{\text{k}}$  \\
    Cologne         & 15.90$^{\text{h}}$ & 26.00$^{\text{k}}$ & 6.50$^{\text{k}}$  
    & 3.51$^{\text{m}}$ 
                    &  7.84$^{\text{k}}$ & 0.291$^{\text{k}}$ \\
    Düsseldorf      & 16.80$^{\text{f}}$ & 28.50$^{\text{g,k}}$ & 7.00$^{\text{k}}$  
    & 3.57$^{\text{m}}$ 
                    &  9.24$^{\text{k}}$ & 0.550$^{\text{k}}$ \\
    Frankfurt (Main)& 22.89$^{\text{a}}$ & 41.50$^{\text{k}}$ & 9.00$^{\text{k}}$  
    & 3.81$^{\text{m}}$ 
                    & 11.63$^{\text{k}}$ & 0.580$^{\text{k}}$ \\
    Hamburg         & 17.40$^{\text{e}}$ & 31.00$^{\text{k}}$ & 6.00$^{\text{k}}$  
    & 3.64$^{\text{m}}$ 
                    & 15.14$^{\text{k}}$ & 0.530$^{\text{k}}$ \\
    Munich          & 20.50$^{\text{b}}$ & 41.00$^{\text{k}}$ & 9.50$^{\text{k}}$  
    & 3.82$^{\text{m}}$ 
                    & 20.96$^{\text{b,k}}$ & 0.760$^{\text{k}}$ \\
    Stuttgart       & 20.40$^{\text{i}}$ & 25.50$^{\text{k}}$ & 9.00$^{\text{k}}$  
    & 3.51$^{\text{m}}$ 
                    &  8.84$^{\text{k}}$ & 0.319$^{\text{k}}$\\
    \hline
    Essen  (B-City) & 12.00$^{\text{e}}$ & 16.00$^{\text{e}}$ &  & & &                   \\
    Leipzig (B-City)& 10.80$^{\text{e}}$ & 15.50$^{\text{e}}$ &  & & &                 \\
    \hline
    A-Cities        & & 34.30$^{\text{n}}$ & & & & 4.03$^{\text{o}}$\\
    B-Cities        & & 15.20$^{\text{n}}$ & & & & 1.2$^{\text{o}}$ \\
    C-Cities        & & 13.40$^{\text{l}}$ & & & & \\
    D-Cities        & & 10.50$^{\text{l}}$ & & & & \\
    All 127 cities  & & & & & & 6.1$^{\text{o}}$\\
    \hline
    \multicolumn{3}{l}{\footnotesize $^{\text{a}}$ Source: \citet{Statista2021c}, Rent 2020} &
    \multicolumn{4}{l}{\footnotesize $^{\text{b}}$ Source: \citet{Statista2021d}, Rent 2019} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{c}}$ Source: \citet{Statista2021e}, Rent 2019} &
    \multicolumn{4}{l}{\footnotesize $^{\text{d}}$ Source: \citet{Statista2021f}, Rent 2020} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{e}}$ Source: \citet{Statista2021g}, Rent 2020} & 
    \multicolumn{4}{l}{\footnotesize $^{\text{f}}$ Source: \citet{Statista2021h}, Rent 2020} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{g}}$ Source: \citet{Statista2021i}, Rent 2020} &
    \multicolumn{4}{l}{\footnotesize $^{\text{h}}$ Source: \citet{Statista2021j}, Rent 2020} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{i}}$ Source: \citet{Statista2021k}, Rent 2019} &
    \multicolumn{4}{l}{\footnotesize $^{\text{j}}$ Source: \citet{Statista2021l}, Rent 2019} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{k}}$ Source: \citet{JLL2021}, Rent 2020} &
    \multicolumn{4}{l}{\footnotesize $^{\text{l}}$ Source: \citet{BNP2021}, Rent 2020} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{m}}$ Source: \citet{JLL2018}, 2018} &
    \multicolumn{4}{l}{\footnotesize $^{\text{j}}$ Source: \citet{Statista2021m}, 2019, 3\% 
    in highest segment} \\
    \multicolumn{3}{l}{\footnotesize $^{\text{o}}$ Source: \citep{FeldEtAl2020}}, 2019 & & & \\
    \hline
    \multicolumn{7}{l}{\footnotesize \parbox{12cm}{Note A-cities account for about 66\% 
    of new rent are in 2019, B-cities for 10\%, C-cities for 5\%. \citep{FeldEtAl2020}}} \\
    \multicolumn{7}{l}{\footnotesize \parbox{12cm}{B-Cities (14): Bochum, Bonn, Bremen, 
    Dresden, Dortmund, Duisburg, Essen, Hannover, Karlsruhe, Leipzig, Mannheim, 
    Nürnberg, Münster, Wiesbaden}}
  \end{tabular}
  \caption{Office rents of new contracts, Germany, 2019 and 2020}  
  \label{tab: officerentsDE}
\end{table}

We do not have any information on the distribution of the rents paid. Therefore, 
we use a very simply approach. We assume that rents in each of the i-City-Segment 
is normally distributed around the mean gross rent but is truncated at the minimum 
and maximum rent level. We have these in the A-city segment. In the B-City segment 
there is no minimum and no mean, while the maximum is taken from the city of Essen 
and the mean from the city of Leipzig. We use the very low minimum from the A-city 
segment also as minimum for the B-city segment. We have only maximum rents for C- 
and D-cities. We use 5 EUR as minimum (slightly lower than in the A-cities).  Then, 
we assume equal distribution of rents in C- and D-cities. Eventually, we draw for 
each i-City segment a share of 10000 random draws from the assumed densities. The 
share is calculated from the share of each segment on all newly rented sqm in 2019/20. 
The share of C- and D-cities is calculated with the assumption that C-cities' 
accumulated share of newly rented sqm is three times as large as the share of D-cities sqm. 


```{r, officerentDE}
# Calculate city types' share on newly rented office space
shareNewlyRentedACities <- 4.029/6.1
shareNewlyRentedBCities <- 1.2/6.1
shareNewlyRentedCCities <- 0.75*(6.1-4.029-1.2)/6.1
shareNewlyRentedDCities <- 0.25*(6.1-4.029-1.2)/6.1

# Importing the dplyr library (to add columns from manipulation of existing data columns)
library(dplyr)
# data base (Table Office Rents Germany)
# note: addcosts of B-C cities is assumed to be 3.5
dfRentDE = data.frame(
  "City" = c("Berlin","Cologne","Dusseldorf","Frankfurt","Hamburg", "Munich","Stuttgart","ACities","BCities","CCities", "DCities"),
  "avgrent" = c(28.700, 15.900, 16.80, 22.89, 17.40, 20.50, 20.400, NaN, NaN, NaN, NaN),
  "upperrent" = c(38.000, 26.000, 28.50, 41.50, 31.00, 41.00, 25.500, 34.30, 15.2, 13.4, 10.5),
  "lowestrent" = c(9.000, 6.500, 7.00, 9.00, 6.00, 9.50, 9.000, NaN, NaN, NaN, NaN),
  "addcosts" = c(3.680, 3.510, 3.50, 3.81, 3.64, 3.82, 3.510, 3.5, 3.5, 3.5,  3.5),
  "available" = c(20.800, 7.840, 9.24, 11.60, 15.14, 20.96,  8.840, NaN,  NaN,  NaN,  NaN),
  "newlyrented" = c(0.999,  0.291,  0.55, 0.58, 0.53, 0.76, 0.319,  4.029, 1.2,  NaN,   NaN)
)
dfRentDE
# gross rents
avggross <- dfRentDE$avgrent + dfRentDE$addcosts
upgross <- dfRentDE$uperrent + dfRentDE$addcosts
lowgross <- dfRentDE$lowerrent + dfRentDE$addcosts
avggross
lowgross
upgross
newavggross <- dfRentDE$newlyrented * avggross
dfRentDE <- mutate(dfRentDE, avgGrossRent = avgrent + addcosts, upperGrossRent = upperrent + addcosts, lowestGrossRent = lowestrent + addcosts)
dfRentDE

### Calculations for A-city type
# an A-city's share of new rented office space
idx <- seq(from = 1, to = 7, by = 1)
dfRentDE <- mutate(dfRentDE, shareNewly = newlyrented/sum(newlyrented[idx],na.rm=TRUE))
# A-cities's average gross rent
SumavgGrossRentACities <- sum(dfRentDE$avgGrossRent[idx] * dfRentDE$shareNewly[idx],na.rm=TRUE) 

# Calculate truncated normal for A-cities
lower1 <- min(dfRentDE$lowestGrossRent[idx],na.rm=TRUE)
lowerA <- lower1
upper1 <- max(dfRentDE$upperGrossRent[idx],na.rm=TRUE)
mean1 <- SumavgGrossRentACities
# lower1 determines the 2.5% percentile(1.96); 
up1 = mean1 + (mean1-lower1) 
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws for share of A-city type
numberA <- round(numberrandom * shareNewlyRentedACities, digits=0)
#checkno <- numberrandom - (numberA + numberB + numberC + numberD)
#### random numbers and plots for A city
set.seed(423)
upper1
parArentDE <- rtruncnorm(numberA, a = lower1, b=upper1, mean = mean1, sd =sd1)
## sequence of values between lower and upper bounds
xgx <- seq(from=lower1, to=upper1, by=0.1)
#xgx
## vector of values of the heigth of the probability distribution for each value of x 
ygx=dtruncnorm(xgx, a=lower1, b=upper1,mean=mean1,sd=sd1)
#ygx
## plot density
plot(xgx, ygx, type = "l", xlab ="ArentDE - rentDE A-cities",ylab = "", 
     main="Truncated Normal Density of parArentADE")
# plot histogram
hist(parArentDE, main="", xlab="rentDE A-cities - random numbers from a 
     truncated normal")

### Calculations for B-city type

# Calculate truncated normal for B-cities
lower1 <- min(lowerA-0.50,na.rm=TRUE)
upper1 <- max(dfRentDE$upperGrossRent[9],na.rm=TRUE)
mean1 <- 1/2 * (upper1 + lower1)
# lower1 determines the 2.5% percentile of a normal distribution 
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws for share of B-city type
numberB <- round(numberrandom * shareNewlyRentedBCities, digits=0)
#### random numbers and plots for B cities
set.seed(123)
parBrentDE <- rtruncnorm(numberB, a = lower1, b=upper1, mean = mean1, sd =sd1)
## sequence of values between lower and upper bounds
xgx <- seq(from=lower1, to=upper1, by=0.1)
#xgx
## vector of values of the heigth of the probability distribution for each value of x 
ygx=dtruncnorm(xgx, a=lower1, b=upper1,mean=mean1,sd=sd1)
#ygx
## plot density
plot(xgx, ygx, type = "l", xlab ="rentDE B-cities",ylab = "", 
     main="Truncated Normal Density of parArentADE")
# plot histogram
hist(parBrentDE, main="", xlab="rentDE B-cities - random numbers from a truncated normal")

# Calculate truncated normal for C-cities
lower1 <- min(lowerA-1,na.rm=TRUE)
upper1 <- max(dfRentDE$upperGrossRent[10],na.rm=TRUE)
mean1 <- 1/2 * (upper1 + lower1)
# lower1 determines the 2.5% percentile of a normal distribution; 
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws for share of C-city type
numberC <- round(numberrandom * shareNewlyRentedCCities,digits=0)
#### random numbers and plots for C cities
set.seed(423)
parCrentDE <- rtruncnorm(numberC, a = lower1, b=upper1, mean = mean1, sd =sd1)
## sequence of values between lower and upper bounds
xgx <- seq(from=lower1, to=upper1, by=0.1)
#xgx
## vector of values of the heigth of the probability distribution for each value of x 
ygx=dtruncnorm(xgx, a=lower1, b=upper1,mean=mean1,sd=sd1)
#ygx
## plot density
plot(xgx, ygx, type = "l", xlab ="rentDE C-cities",ylab = "", 
     main="Truncated Normal Density of parArentADE")
# plot histogram
hist(parCrentDE, main="", xlab="rentDE C-cities - random numbers from a truncated normal")

# Calculate truncated normal for D-cities
lower1 <- min(lowerA-1.5,na.rm=TRUE)
lower1
upper1 <- max(dfRentDE$upperGrossRent[11],na.rm=TRUE)
mean1 <- 1/2 * (upper1 + lower1)
# lower1 determines the 2.5% percentile of a normal distribution; 
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws for share of D-city type
numberD <- numberrandom - numberA - numberB - numberC
#### random numbers and plots for D cities
set.seed(423)
parDrentDE <- rtruncnorm(numberD, a = lower1, b=upper1, mean = mean1, sd =sd1)
## sequence of values between lower and upper bounds
xgx <- seq(from=lower1, to=upper1, by=0.1)
#xgx
## vector of values of the heigth of the probability distribution for each value of x 
ygx=dtruncnorm(xgx, a=lower1, b=upper1,mean=mean1,sd=sd1)
#ygx
## plot density
plot(xgx, ygx, type = "l", xlab ="rentDE D-cities",ylab = "", 
     main="Truncated Normal Density of parArentADE")
# plot histogram
hist(parDrentDE, main="", xlab="rentDE D-cities - random numbers from a truncated normal")

### 
parrentDE <- c(parArentDE,parBrentDE,parCrentDE,parDrentDE)
hist(parrentDE, breaks=60, main="Frequency office rents DE", xlab=" rent DE - random numbers", ylab ="")
png("imgrentDE.png")
hist(parrentDE, breaks=60, main="Frequency office rents DE", xlab=" rent DE - random numbers", ylab ="")
summary(parrentDE)
# random draws from parrentde
set.seed(423)
parRentDE <- sample(parrentDE)
mean2 <- mean(parRentDE)
mean2
```



### 4.1.2 U.S. (rmonthUS)

\begin{table}[htbp]
  \centering
  \footnotesize
  \begin{tabular}{r|r|l|l|c|c|c|c} 
  \hline \hline
  Rank      & Rank     &      &          & max gross cost$^{\text{a}}$ & 
  net rent$^{\text{b}}$ & avg.rent A$^{\text{d}}$ & avg.rent 2020$^{\text{e}}$ \\
  world & national & City & District            & USD/sqft p.a.  &  USD/sqft p.a. 
  &  USD/sqft p.a. & USD/sqft p.a.\\
  \hline
  4 & 1 & New York        & Midtown Manhattan       & 212$^{\text{b}}$ 
  & 170$^{\text{c}}$ & 85$^{\text{f}}$ & 83.82$^{\text{f}}$ \\
  7 & 2 & New York        & Midtown South Manh.\ & 182$^{\text{b}}$ 
  & 152$^{\text{c}}$ & 95$^{\text{f}}$ & 88.47$^{\text{f}}$ \\
  11 & 3 & San Francisco  & Silicon Valley          & 162$^{\text{b}}$ 
  & 135$^{\text{c}}$ & 69.95         & 85.87$^{\text{g}}$\\
  13 & 4 & San Francisco  & city                    & 118$^{\text{b}}$ 
  & 85$^{\text{c}}$  & 104.79        & 85.87$^{\text{g}}$\\
  17 & 5 & Boston         & Cambridge               & 103$^{\text{b}}$ 
  & 85$^{\text{c}}$  &               & \\ 
  18 & 6 & New York       & Downtown Manhattan      & 107$^{\text{b}}$ 
  & 87$^{\text{c}}$  & 68$^{\text{f}}$ & 64.64$^{\text{f}}$\\
  20 & 7 & Los Angeles    & Westside                & 104$^{\text{b}}$ 
  & 86$^{\text{c}}$  & 39.82         & \\
  17 & 8 & Boston         & city                    & 100$^{\text{b}}$ 
  & 78$^{\text{c}}$  & 71.20         & 44.06$^{\text{g}}$ \\
  22 & 9 & Washington D.C.& Downtown                & 88$^{\text{b}}$ 
  & 65$^{\text{c}}$  & 60.39         & 59.42$^{\text{g}}$\\
  & 10 & Austin           & city                    & 87$^{\text{b}}$  
  & 60$^{\text{c}}$  & 52.85         & 49.93 \\
  42 & 11 & Seattle       & Downtown                & 66.47          & 51.50          
  &               & 45.59$^{\text{g}}$ \\
  45 & 12 & Houston       & Downtown                & 64.60          &                
  & 45.67         & 31.97$^{\text{g}}$\\
  46 & 13 & Seattle       & Suburban                & 64.20          & 43.16          
  &               & 45.59$^{\text{g}}$\\
  & 14 & Chicago          & Downtown                & 76$^{\text{b}}$  & 50$^{\text{c}}$  
  & 48.81         & 43.99 \\
  & 15 & Houston          & Suburban                & 56.88          & 32$^{\text{c}}$  
  &32.66          & 31.97$^{\text{g}}$\\
  & 16 & Dallas           & Downtown                & 56.25          & 42$^{\text{b}}$  
  & 29.21         & 31.08$^{\text{g}}$ \\
  & 17 & Los Angeles      & Downtown                & 69$^{\text{b}}$  & 48$^{\text{c}}$  
  & 46.69         & \\
  
  & 18 & Denver           & Downtown                & 51.50          & 40$^{\text{c}}$  
  &               & 31.87$^{\text{g}}$\\
  & 19 & Atlanta          & Buckhead and Midtown    & 50.14          &                
  & 37.60         & 29.35$^{\text{g}}$ \\
  & 20 & Boston           & Suburans                & 48.06          &                
  & 31.49         & 44.06$^{\text{g}}$\\
  & 21 & Dallas           & Suburban                & 45.93          &                
  & 31.83         & 31.08$^{\text{g}}$\\
  & 22 & Auckland         & city                    & 40$^{\text{b}}$  & 30$^{\text{c}}$  
  &               & \\
  & 23 & Atlanta          & Suburban                & 37.76          &                
  & 29.41         & 29.35$^{\text{g}}$\\
  & 24 & Chicago          & Suburban                & 30.50          &                
  &               & 25.93 \\
  & 25 & Denver           & Suburban                & 30.25          &                
  & 28.56         & 31.87$^{\text{g}}$\\
  \hline 
  \multicolumn{8}{l}{\footnotesize \parbox{13cm}{Occupancy cost include service charges, 
  taxes. 
  They are standardized on a net internal area basis. Prime office occupance costs are 
  costs for the highest-quality office space in a prime location}}\\
  \multicolumn{8}{l}{\footnotesize \parbox{13cm}{Top 1: Hongkong 208.67, Top 2: 
  London (West End) 222.70, Top 50 Frankfurt: 61.77} }\\
  \multicolumn{8}{l}{\footnotesize $^{\text{a}}$ Source: \citet{CBRE2019}} \\
    \multicolumn{8}{l}{\footnotesize Source: $^{\text{b}}$ \citet{JLL2019}} \\
    \multicolumn{8}{l}{\footnotesize Source: $^{\text{c}}$ Approximation from \citet{JLL2019}} \\
        \multicolumn{8}{l}{\footnotesize Source: $^{\text{d}}$ \citet{Colliers2019}}\\
         \multicolumn{8}{l}{\footnotesize Source: $^{\text{d}}$ \citet{JLL2020a}} \\
         \multicolumn{8}{l}{\footnotesize Source: $^{\text{f}}$ \citet{JLL2020b} in 2020} \\
         \multicolumn{8}{l}{\footnotesize Source: $^{\text{g}}$ average over the whole city}
  \end{tabular}
  \caption{Prime Office Occupancy Cost - top U.S. City Districts} \label{tab: grossrentUS}
\end{table}

```{r, rentUS} 
# sqm per sqft

dfRentUS = data.frame(
  "RankNational" = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25),
  "City" = c("New York Mid Manh", "New York Mid South Manh", "San Francisco Silicon Valley", 
             "San Francisco city", "Boston Cambridge", "New York Downtown Manh", 
             "Los Angeles Westside", "Boston city", "Washington D.C. Downtown", 
             "Austin city", "Seattle Downtown", "Houston Downtown", "Seattle Suburban", 
             "Chicago Downtown", "Houston Suburban", "Dallas Downtown", 
             "Los Angeles Downtown", "Denver Downtown", "Atlanta Buckhead & Midtown", 
             "Boston Suburban", "Dallas Suburban", "Auckland city", "Atlanta Suburban", 
             "Chicago Suburban", "Denver Suburban"),
  "occupancycost" = c(212, 182, 162, 118, 103, 107, 104, 100,  88, 87, 66.47, 64.60, 
                      64.20, 76, 56.88, 56.25, 69,
  51.50, 50.14, 48.06, 45.93, 40, 37.76, 30.50, 30.25))
  "net rent" = c(170, 152, 135, 85, 85, 87, 86, 78, 65, 60, NaN, NaN, NaN, 50, 32, 
                 42, 48, 40, NaN, NaN, NaN, 30, NaN, NaN, NaN)
dfRentUS
# rents in EUR per sqm per month
dfRentUS <- mutate(dfRentUS, maxGrossRent = occupancycost * sqmsqft * EURDollar/12)
dfRentUS$maxGrossRent
lower1 <- min(dfRentUS$maxGrossRent)
upper1 <- max(dfRentUS$maxGrossRent)
med1 <- median(dfRentUS$maxGrossRent)
med1
mean1 <- 1/2 * (upper1 + lower1)
lower1
upper1
mean1
# lower1 determines the 2.5% percentile of a normal distribution; 
sd1 <- (lower1-mean1)/qnorm(0.025)
sd1
# 2. 10000 random draws for share of D-city type
#### random numbers and plots for D cities
set.seed(423)
parRentUS <- rtruncnorm(numberrandom, a = lower1, b=upper1, mean = mean1, sd =sd1)
meanparRentUS <- mean(parRentUS)
meanparRentUS
## sequence f values between lower and upper bounds
xgx <- seq(from=lower1, to=upper1, by=0.1)
#xgx
## vector of values of the heigth of the probability distribution for each value of x 
ygx=dtruncnorm(xgx, a=lower1, b=upper1,mean=mean1,sd=sd1)
#ygx
## plot density
plot(xgx, ygx, type = "l", xlab ="rentUS",ylab = "", 
     main="Truncated Normal Density of parRentUS")
# plot histogram
hist(parRentUS, breaks=60, main="", xlab="rentUS - random numbers from a truncated normal")
png("imgrentUS.png")
hist(parRentUS, breaks=60, main="", xlab="rentUS - random numbers from a truncated normal")



```



## 4.2 sqmemployee (sqm of office space per employee)

### 4.2.1 Germany (sqmemployeeDE)

\citet{HengerEtAl2017}

\begin{table}[htb]
  \centering
  \begin{tabular}{c|c|c|c|c}
    \multicolumn{5}{c}{$m^2$ Nutzfläche je Beschäftigte$^{\text{a}}$} \\
    \hline
    Branchen  & \multicolumn{4}{c}{Kreistyp$^{\text{b}}$}\\
             & A-Städte & B-Städte & sonst. Großstädte & Durchschnitt \\
             \hline
    Banken/Finanz  & 31 & 24,6 & 23 & 24,1 \\
    Bau,Immobilien & 32,3 & 25,6 & 24 & 25,1 \\
    EDV & 28,4 & 22,5 & 21,1 & 22 \\
    Industrie & 25,3 & 20,1 & 18,8 & 19,7 \\
    Transport & 26,2 & 20,8 & 19,5 & 20,4 \\
    Dienstleistung & 33,5 & 26,6 & 24,9 & 26 \\
    Handel & 34,9 & 27,7 & 25,9 & 27,1 \\
    \hline
    Durchschnitt & 30,9 & 24,5 & 22,9 & 24 \\
    \hline
    \multicolumn{5}{l}{$^{\text{a}}$ see \cite{HengerEtAl2017}} \\
    \multicolumn{5}{l}{$^{\text{b}}$ \parbox{13cm}{\footnotesize A-Städte 
    (wichtigste Bürostandorte): Berlin, Düsseldorf, Frankfurt (Main), Hamburg, 
    Köln, München, Stuttgart. B-Städte: u.a. Bonn, Dortmund, Dresden, Essen, 
    Hannover, Leipzig, Mannheim, Wiesbaden. sonst. Großstädte: weitere kreisfreie 
    Städte > 100000 Einwohner}}
  \end{tabular}
  \caption{Office space per employee in German cities} \label{tab: office space DE}
\end{table}


```{r, sqmemployeeDE}
# random numbers for office space per employee
set.seed(555)
sqmemployeeDE <- runif(numberrandom, min = 18.8, max = 34.9)
mean1 <- mean(sqmemployeeDE)
mean1

```



### 4.2.2 U.S. (sqmemployeeUS)


U.S.\ (statista} 138 square ft. (12.8 square meter) in the Americas in 2017, 
in 2012 it was about 176 square feet according to CoreNetGlobal 
\citep[cited in][]{Cipolla2020}. CoreNet Global expected decline to 100 square ft 
\citep[cited in][]{PRNewswire2012}

The real eastate firm Austin Tenant Advisors guess that 150-175 square ft. per 
employee is US average \citep{Nathan2020} .

100-300 sqf (9.29-27.87 sqm) suggested by Housont Installation \citep{Twardowski2019} 

Trend in coworking - strong increase. 

We use a uniform distribution over 12-15 sqm

```{r, sqmemployeeUS}
# random numbers for office space per employee
set.seed(555)
sqmemployeeUS <- runif(numberrandom, min = 9.29, max = 27.87)
mean1 <- mean(sqmemployeeUS)
mean1
```


# 5. Other Components: Delay Costs



* delayA (delay costs with contract A)



# 6. Non-data driven Parameters

* delayB (delay costs with contract B - not from data)
* beta (productivity of in-vehicle work - not from data)
* s_drive (share of driving during in-vehicle work - not from data)



```{r, FinalDataPrintToGDXfileDE}

#  Generate GDX-File only from data calculated in R
idvar <- c(1:10000)
# matrix of random data - database of random data
numb = 10000;
idlist <- list(name='id_r',uels=list(idvar),ts='MC run',type='set') 
mc_gkm <- list(name='mc_gkm',val=as.array(pargkmDE), uels=list(idvar),dim=1,
               form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
            type='parameter',domains='id_r') 
mc_gs <- list(name='mc_gs',val=as.array(pargsDE), uels=list(idvar),dim=1,
              form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_gd <- list(name='mc_gd',val=as.array(pargdDE), uels=list(idvar),dim=1,
              form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_xbar <- list(name='mc_xbar',val=as.array(distanceDE), uels=list(idvar),dim=1,
                form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_parambDE <- list(name='mc_parambDE',val=as.array(parambDE), uels=list(idvar),dim=1,
                    form='full',ts='parameter to deterine tkm [h:km]',  
                    type='parameter',domains='id_r') 
mc_sqmemployee <- list(name='mc_sqmemployee',val=as.array(sqmemployeeDE), uels=list(idvar),dim=1,form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_rmonth <- list(name='mc_rmonth',val=as.array(parRentDE), uels=list(idvar),dim=1,
                  form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_avgproduct <- list(name='mc_avgproduct',val=as.array(avgprodDE), uels=list(idvar),
                      dim=1,form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_wage <- list(name='mc_wage',val=as.array(wageDE), uels=list(idvar),dim=1,form='full',
                ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
wgdx.lst('MC_paramDE',list(idlist,mc_gkm,mc_gs,mc_gd,mc_xbar,mc_parambDE,
                           mc_sqmemployee,mc_rmonth,mc_avgproduct,mc_wage))
gdxInfo('MC_paramDE',dump=FALSE,returnList=TRUE, returnDF=TRUE)

# means
id_l = 1
idmvar = id_l
am_wage <- list(name='am_wage',val=as.array(mean(wageDE)), uels=list(idmvar),
                dim=1,form='full',ts='mean gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_l') 
mwage <- mean(wageDE)*8

```


```{r, Descriptives}
idvar <- c(1:10000)
# matrix of random data - database of random data
#  Generate GDX-File only from data calculated in R
idvar <- c(1:10000)
# matrix of random data - database of random data
numb = 10000;
idlist <- list(name='id_r',uels=list(idvar),ts='MC run',type='set') 
mc_gkmUS <- list(name='mc_gkmUS',val=as.array(pargkmUS), uels=list(idvar),dim=1,
                 form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
            type='parameter',domains='id_r') 
mc_gsUS <- list(name='mc_gsUS',val=as.array(pargsUS), uels=list(idvar),dim=1,
                form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_gdUS <- list(name='mc_gdUS',val=as.array(pargdUS), uels=list(idvar),dim=1,
                form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_xbarUS <- list(name='mc_xbarUS',val=as.array(distanceUS), uels=list(idvar),dim=1,
                  form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_parambUS <- list(name='mc_parambUS',val=as.array(timekmUS), uels=list(idvar),dim=1,
                    form='full',ts='parameter to determine tkm [h/km]',
               type='parameter',domains='id_r') 
mc_sqmemployeeUS <- list(name='mc_sqmemployeeUS',val=as.array(sqmemployeeUS), uels=list(idvar),dim=1,form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_rmonthUS <- list(name='mc_rmonthUS',val=as.array(parRentUS), uels=list(idvar),dim=1,
                    form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_avgproductUS <- list(name='mc_avgproductUS',val=as.array(avgprodUS), uels=list(idvar),dim=1,form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
mc_wageUS <- list(name='mc_wageUS',val=as.array(wageUS), uels=list(idvar),dim=1,
                  form='full',ts='gross monetary avg. travel costs employee [EUR:km]',
               type='parameter',domains='id_r') 
wgdx.lst('MC_paramUS',list(idlist,mc_gkmUS,mc_gsUS,mc_gdUS,mc_xbarUS,mc_parambUS,
                           mc_sqmemployeeUS,mc_rmonthUS,mc_avgproductUS,mc_wageUS))
gdxInfo('MC_paramUS',dump=FALSE,returnList=FALSE, returnDF=TRUE)

mwage <- mean(wageUS)*8

```


```{r, FinalPrintToFile_US, warning=FALSE, results='asis'}
# summary statistics
# generate database
paramDE.frame <- data.frame(pargkmDE,pargsDE,pargdDE,distanceDE,
                           sqmemployeeDE,parRentDE,wageDE,timekmDE,avgprodDE)
paramUS.frame <- data.frame(pargkmUS,pargsUS,pargdUS,distanceUS,
                           sqmemployeeUS,parRentUS,wageUS,timekmUS,avgprodUS)

library(stargazer)
correlation.matrix <- cor(paramDE.frame[,c('pargkmDE','pargsDE','pargdDE','distanceDE',
                           'sqmemployeeDE','parRentDE','wageDE','timekmDE')])
stargazer(correlation.matrix, title="Correlation Matrix DE",type ="latex", no.space = TRUE, 
          column.sep.width = "3pt", font.size = "scriptsize")
correlation.matrix <- cor(paramUS.frame[,c('pargkmUS','pargsUS','pargdUS','distanceUS',
                           'sqmemployeeUS','parRentUS','wageUS','timekmUS')])
stargazer(correlation.matrix, title="Correlation Matrix US",type ="latex", no.space = TRUE, 
          column.sep.width = "3pt", font.size = "scriptsize")

```

\thebibliography{99999999999999999999999999999999999999999999}

\bibitem[Association(2020)]{AAA2020} A.A.A., 2020. Your Driving Costs 2020.

\bibitem[ADAC(2020a)]{ADAC2020a} ADAC (2020a) from "Kostenvergleich e-Fahrzeuge 
+ Plug-in Hybride gegen Benziner und Diesel", 2020. 
\href{https://assets.adac.de/image/upload/v1594909696/ADAC-eV/KOR/Text/PDF/E-AutosVergleich_joxjsi.pdf}{
\color{blue}ADAC2020a\color{black}}

\bibitem[ADAC(2020b)]{ADAC2020b} ADAC, 2020b. Berechnungsgrundlagen für die standardisierte 
Autokostenberechnung.

\bibitem[BNP(2021)]{BNP2021} BNP Paribas Real Estate, 2021. Property Report: 
Büromarkt Deutschland
\href{https://www.realestate.bnpparibas.de/marktberichte/bueromarkt/deutschland-property-report-2020/die-deutschen-buerostandorte-im-ueberblick}{\underline{$\text{BNP2021}$}}

\bibitem[BTS(2017)]{BTS2017} Bureau of Transportation Statistiscs (BTS), 2017. 
National Household Travel Survey `Stretch Commute' Quick Facts. \href{https://www.bts.gov/statistical-products/surveys/national-household-travel-survey-stretch-commute-quick-facts}{$\underline{\text{Quick Facts 2017}}$} accessed, 23.03.2021

\bibitem[BTS(2003)]{BTSt2003} Bureau of Transportation Statistics (BTS), 2003. 
Quick Facts. \href{https://www.bts.gov/bts/sites/rita.dot.gov.bts/files/publications/omnistats/volume_03_issue_04/pdf/entire.pdf}{$\underline{\text{Quick Facts 2003}}$} accessed, 23.03.2021

\bibitem[Burd et al.(2021)]{BurdEtAl2021} Burd, C., Burrows, M., McKenzie, B., 2021. 
Travel Time to Work in the United States: 2019. American Community Survey Reports, U.S.\ Census Bureau.



\bibitem[Cipolla(2020)]{Cipolla2020} Cipolla J, 2020. How much office space per 
employee do you need?%\href{https://www.squarefoot.com/blog/office-space-per-employee}{$\underline{\text{Cipolla 2020}}$}

\bibitem[Compostella et al.(2020)]{CompostellaEtAl2020} Compostella, J., Fulton, L.M., 
De Kleine, R., Kim, H.C., Wallington, T.J., 2020. Near- (2020) and long-term (2030/2035) 
costs of automated, electrified, and shared mobility in the United States. 
Transport Policy 85, 54--66.

\bibitem[Colliers(2019)]{Colliers2019} Colliers, 2019. Q4 2019 Office Market Outlook. 
U.S. Research Outlook.

\bibitem[Dauth and Haller(2018)]{DauthHaller2018} Dauth W, Haller P, 2018. 
Berufliches Pendeln zwischen Wohn- und Arbeitsort: Klarer Trend zu längeren 
Pendeldistanzen. iab (10/2018), 13.

\bibitem[Deloitte(2019)]{Deloitte2019} Deloitte, 2019. Urbane Mobilität und 
autonomes Fahren im Jahr 2035 -- Welche Veränderungen durch Robotaxis auf 
Automobilhersteller, Städte, und Politik zurollen.

\bibitem[DeStatis(2021)]{DeStatis2021} DeStatis, 2021. Earnings. Minimum wages. 
\href{https://www.destatis.de/EN/Themes/Labour/Earnings/Minimum-Wages/_node.html}{DeStatis minimum wage} 
accessed 24.03.2021

\bibitem[DeStatis(2018)]{DeStatis2018} DeStatis, 2018. Verdienststrukturerhebung -- 
Ergebnisse für Deutschland. Fachserie 16, Heft 1 2018. \href{https://www.destatis.de/DE/Themen/Arbeit/Verdienste/Verdienste-Verdienstunterschiede/Publikationen/Downloads-Verdienste-und-Verdienstunterschiede/verdienststrukturerhebung-heft-1-2162001189004.html}
{Destatis FS16.1 2018} accessed 24.03.2021

\bibitem[DeStatis(2017)]{DeStatis2017} DeStatis, 2017. Verdienste auf einen Blick. 
\href{https://www.destatis.de/DE/Themen/Arbeit/Verdienste/Verdienste-Verdienstunterschiede/Publikationen/Downloads-Verdienste-und-Verdienstunterschiede/broschuere-verdienste-blick-0160013179004.pdf?__blob=publicationFile}{DeStatis Verdienste} accessed 24.03.2021

\bibitem[Dingel and Neiman(2020)]{DingelNeiman2020} Dingel, J.I., Neiman, B., 2021. 
How many jobs can be done from home? NBER working paper 26948. 

\bibitem[Feld et al.(2020]{FeldEtAl2020})] Feld LP, Schulten A, Simons H, Wandzik C, 
Gerling M, 2020. Frühjahrsgutachten der Immobilienwirtschaft 2020 des Rates der 
Immobilienweisen. Im Auftrag von ZIA, Berlin. \href{https://zia-cloud.de/data/public/d5a531}
{ZIA2020} accessed 24.03.2021

\bibitem[Gerike et al.(2020)]{GerikeEtAl2020} Gerike, R., Hubrich, S., Ließke, F., 
Wittig, S., Wittwer, R., 2020. Tabellenbericht zum Forschungsprojket `Mobilität in 
Städten -- SRV 2018' in Berlin. TU Dresden. \href{https://tu-dresden.de/srv} 
accessed 31.05.2021

\bibitem[Geotab (2018)]{Geotab2018} Geotab, 2018. Gridlocked cities: traffic 
patterns revealed across 20 major U.S. cities. \href{https://www.geotab.com/press-release/traffic-congestion-patterns/}{GEOTAB 2018} 
accessed 31.05.2021

\bibitem[Gimenéz-Nadal et al.(2020)]{GimenezNadal2020} Giménez-Nadal J.I., Molina J.A., 
Velilla J., 2020. Trends in commuting time of European workers: A cross-country analysis. 
IZA Working Paper DP No. 12916.

\bibitem[Gould(2020)]{Gould2020} Gould, E., 2020. State of Working America Wages 2019. 
A story of slow, uneven, and unequal wage growth over the last 40years. Economic Policy 
Institute, Washington D.C.
\href{https://epi.org/183498}{https://epi.org/183498} accessed 24.03.2021

\bibitem[Henger et al.(2017)]{HengerEtAl2017} Henger R, Scheunemann H, Barthauer M, 
Giesemann C, Hude M, Seipelt B, Toschka A, 2017. Büroimmobilien: Energetischer 
Zustand und Anreize zur Steigerung der Energieeffizienz, Tech. Rep., Deutsche Energie-Agentur GmbH.

\bibitem[IEA(2020)]{IEA2020} IEA, 2020. Key World Energy Statistics 2020, p. 81.

\bibitem[JLL(2021)]{JLL2021} JLL, 2021. Büromarktüberblick Big 7/4.Quartal 2020. \href{https://www.jll.de/content/dam/jll-com/documents/pdf/research/emea/germany/de/Bueromarktueberblick-JLL-Deutschland.pdf}{$\underline{\text{JLL 2021}}$} accessed 24.03.2021


\bibitem[JLL(2020a)]{JLL2020a} JLL, 2020a. Office Outlook
\href{https://www.us.jll.com/content/dam/jll-com/documents/pdf/research/Q4-2020-US-Office-Outlook.pdf}
{$\underline{\text{JLL 2020a}}$} accessed 24.03.2021

\bibitem[JLL(2020b)]{JLL2020b} JLL, 2020a. New York Q4 2019, Quarterly Office Outlook
\href{https://www.us.jll.com/content/dam/jll-com/documents/pdf/research/jll-us-new-york-office-outlook-q4-2019.pdf}{$\underline{\text{JLL 2020b}}$} accessed 24.03.2021


\bibitem[JLL(2019)]{JLL2019} JLL, 2019. Global Premium Office Rent Tracker. 
\href{https://www.us.jll.com/content/dam/jll-com/documents/pdf/research/jll-global-premium-office-rent-tracker-q4-2019.pdf}{$\underline{\text{JLL 2019}}$} accessed 24.03.2021

\bibitem[JLL(2018)]{JLL2018} JLL, 2018. Büro-Nebenkosten leicht rückläufig -- OSCAR Analyse von JLL. \href{https://www.jll.de/de/presse/jll-oscar-analyse-buero-nebenkosten-leicht-ruecklaeufig}
{$\underline{\text{JLL 2018}}$} accessed 24.03.2021

\bibitem[KraftStg(2002)]{KraftStg2002} KraftStG 2002. Einzelnorm (n.d.).
\href{https://www.gesetze-im-internet.de/kraftstg/__9.html}{$\underline{\text{KraftStg 2002}}$} 
accessed 24.03.2021

\bibitem[Maye(2019)]{Maye2019} Maye, A., 2019. No-vacation nation, revised. CEPR

\bibitem[Nathan(2020)]{Nathan2020} Nathan, 2020. What is the average square footage of 
office space per person. 
(\href{https://www.austintenantadvisors.com/blog/what-is-the-average-square-footage-of-office-space-per-person/}
{$\underline{\text{Nathan 2020}}$}) accessed 25.05.2021

\bibitem[OECD(2021)]{OECD2021} OECD.Stat 
(\href{https://stats.oecd.org/Index.aspx?DataSetCode=LFS_D}) 
accessed 22.03.2021

\bibitem[OECD(2020)]{OECD2020} OECD, 2020. Taxing Wages 2020. 

\bibitem[OECD(2018)]{OECD2018} OECD, 2018. OECD Employment Outlook 2018, OECD.
\href{https://www.oecd-ilibrary.org/employment/oecd-employment-outlook-2018_empl_outlook-2018-en}
{$\underline{\text{OECD 2018}}$} accessed 24.03.2021

\bibitem[PR Newswire(2012)]{PRNewswire2012} PR Newswire, 2012. Office space per 
worker will drop to 100 square feet of below for many companies within five years, 
according to new research from CoreNet Global.
(cited in:  
\href{https://www.prnewswire.com/news-releases/office-space-per-worker-will-drop-to-100-square-feet-or-below-for-many-companies-within-five-years-according-to-new-research-from-corenet-global-140702483.html}
{$\underline{\text{rnewswire 2012}}$}: news from CoreNet Global) accessed 25.05.2021

\bibitem[Rietveld et al.(1999)]{Rietveld1999} Rietveld, P., Zwart, B., van Wee, B., 
van den Hoorn, T., 1999. On the relationship between travel time and travel distance 
of commuters. Annals of Regional Science 33, 269--287.

\bibitem[Statista(2021a)]{Statista2021a} Statista (2021a) O average, how long is 
your daily commute to work/school/university (one way?) \href{https://www.statista.com/forecasts/998812/duration-of-daily-commute-in-germany}
{$\underline{\text{Statista 2021a}}$} accessed 24.03.2021 

\bibitem[Statista(2021b)]{Statista2021b} Statista (2021b) Durchschnittsmiete in 
den Top 5-Bürozentren in Deutschland im 4.Quartal der Jahre 2014 und 2015. 
\href{https://de.statista.com/statistik/daten/studie/77146/umfrage/durchschnittliche-miete-fuer-bueroflaechen-in-staedten-2008-und-2009/}{$\underline{\text{Statista 2021b}}$} accessed 24.03.2021 

\bibitem[Statista(2021c)]{Statista2021c} Statista (2021c) Mietpreise für Büroflächen 
in Frankfurt am Main bis 2020
\href{https://de.statista.com/statistik/daten/studie/261013/umfrage/entwicklung-der-mietpreise-fuer-bueroflaechen-in-frankfurt-am-main/}{$\underline{\text{Statista 2021c}}$} accessed 25.03.2021

\bibitem[Statista(2021c)]{Statista2021d} Statista (2021d) Entwicklung der 
Durchschnittsmieten für Büroflächen in München von 2004 bis 2019
\href{https://de.statista.com/statistik/daten/studie/209635/umfrage/entwicklung-der-mietpreise-fuer-bueroflaechen-in-muenchen/}{$\underline{\text{Statista 2021d}}$} accessed 25.03.2021

\bibitem[Statista(2021e)]{Statista2021e} Statista (2021e) Entwicklung der 
Durchschnittsmieten für Büroflächen in Berlin 
\href{https://de.statista.com/statistik/daten/studie/177523/umfrage/entwicklung-der-mietpreise-von-bueroflaechen-in-berlin-seit-2003/}{$\underline{\text{Statista 2021e}}$} accessed 25.03.2021

\bibitem[Statista(2021f)]{Statista2021f} Statista (2021f) Entwicklung der 
Spitzenmiete für Büroflächen in Berlin von 2008 bis 2020
\href{https://de.statista.com/statistik/daten/studie/183180/umfrage/entwicklung-der-spitzenmiete-im-bueromarkt-in-berlin-seit-2008/}{$\underline{\text{Statista 2021f}}$} accessed 25.03.2021


\bibitem[Statista(2021g)]{Statista2021g} Statista (2021g) Entwicklung der Mietpreise 
für Büroflächen in Hamburg von 2003 bis 2020
\href{https://de.statista.com/statistik/daten/studie/177383/umfrage/entwicklung-der-mietpreise-von-bueroflaechen-in-hamburg-seit-2003/}{$\underline{\text{Statista 2021g}}$} accessed 25.03.2021

\bibitem[Statista(2021h)]{Statista2021h} Statista (2021h) Entwicklung der 
Durchschnittsmiete für Büroflächen in Düsseldorf bis 2020
\href{https://de.statista.com/statistik/daten/studie/625728/umfrage/mietpreis-fuer-bueroflaechen-in-duesseldorf/}{$\underline{\text{Statista 2021h}}$} accessed 25.03.2021

\bibitem[Statista(2021i)]{Statista2021i} Statista (2021i) Entwicklung der 
Spitzenmiete für Büroflächen in Düsseldorf von 2009 bis zum 1. Halbjahr 2020
\href{https://de.statista.com/statistik/daten/studie/368473/umfrage/spitzenmiete-fuer-bueroflaechen-in-duesseldorf/}{$\underline{\text{Statista 2021i}}$} accessed 25.03.2021

\bibitem[Statista(2021j)]{Statista2021j} Statista (2021j) Entwicklung der 
Mietpreise für Büroflächen in Köln von 2003 bis 2020
\href{https://de.statista.com/statistik/daten/studie/177552/umfrage/entwicklung-der-mietpreise-von-bueroflaechen-in-koeln-seit-2003/}{$\underline{\text{Statista 2021j}}$} accessed 25.03.2021

\bibitem[Statista(2021k)]{Statista2021k} Statista (2021k) Entwicklung der 
Durchschnittsmiete für Büroflächen in Stuttgart von 2001 bis 2019
\href{https://de.statista.com/statistik/daten/studie/586252/umfrage/mietpreise-fuer-bueroflaechen-in-stuttgart/}{$\underline{\text{Statista 2021k}}$} accessed 25.03.2021

\bibitem[Statista(2021l)]{Statista2021l} Statista (2021l) Entwicklung der 
Spitzenmiete für Büroflächen in Stuttgart von 2001 bis 2019
\href{https://de.statista.com/statistik/daten/studie/583031/umfrage/spitzenmiete-fuer-bueroimmobilien-in-stuttgart/}{$\underline{\text{Statista 2021l}}$} accessed 25.03.2021

\bibitem[Statista(2021m)]{Statista2021m} Statista (2021m) Büroflächen -- 
Bestand nach Großestädten in Deutschland 2019/2020
\href{https://de.statista.com/statistik/daten/studie/244653/umfrage/bueroflaechengroesse-nach-deutschen-grossstaedten/}{$\underline{\text{Statista2021m.com}}$} accessed 25.03.2021

\bibitem[Statista(2020)]{Statista2020} Statistia (2019) Durchschnittliche 
Geschwindkeiten im Automobilverkehr in ausgewählten deutschen Städten im Jahre 2018. \href{https://de.statista.com/statistik/daten/studie/994676/umfrage/innerstaedtische-durchschnittsgeschwindigkeit-im-autoverkehr-in-deutschen-staedten/}{$\underline{\text{Statista 2019}}$} accessed 27.05.2021

\bibitem[StromStG(2020)]{StromStG} StromStG 2020.
\href{https://www.gesetze-im-internet.de/stromstg/index.html}
{$\underline{\text{StromStG 2020}}$} accessed 24.03.2021

\bibitem[Twardowski(2019)]{Twardowski2019} Twardowski T, 2019. How much office 
space do you need? 
\href{https://www.houstoninstallation.com/blog/how-much-office-space-do-i-need}
{$\underline{\text{Twardowski 2019}}$} accessed: 25.05.2021.

\bibitem[US BoL(2021a)]{USBoL2021a} U.S.\ Bureau of Labor Statistics, BoL, 2020.  
\href{https://data.bls.gov}{$\underline{\text{BoL 2020}}$} accessed: 22.03.2021.

\bibitem[US BoL(2021b)]{USBoL2021b} U.S.\ Bureau of Labor Statistics, BoL, 2020.  

\bibitem[US DoL(2021)]{USDoL2021} U.S.\ Department of Labor (US DoL), 2021.
\href{https://www.dol.gov/general/topic/wages/minimumwage}{$\underline{\text{DoL}}$} 
accessed 24.03.2021

\bibitem[US Department Transport(2020)]{USDepTr2020} U.S.\ Department of Transportation, 
BoTS, 2020. Transportation Statistics Annual Report 2020. 
\href{https://rosap.ntl.bts.gov/view/dot/53936}{$\underline{\text{U.S.\ BoTS 2020}}$} 
accessed: 20.03.2021.



\bibitem[CBRE(2019)]{CBRE2019} CBRE, 2019. 2019 Global prime office occupancy costs. 
and \href{http://cbre.vo.llnwd.net/grgservices/secure/2019%20CBRE%20POOC_Q9bx.pdf?e=1617101862&h=d62ccb3196eeda4e0b1adeb756c3d94d}{\color{blue}CBRE 2019} accessed, 30.03.2021



